---
title: "Lab 5"
author: "Katie Pietrucha"
date: "10/25/2021"
output: 
  html_document: 
    theme: cerulean
    toc: yes
    code_folding: hide
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals

In this section, we'll use the `t.test()` function to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values, then learn to use `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible too.

```{r}
# Create a mock sample
otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths)

# Find the standard deviation
otter_sd <- sd(otter_lengths)
```

#### What does 95% CI mean? If we took multiple samples from this population and calculated a CI for each, we would expect that 95% of CIs would contain true population mean.

Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n = 8) with a 95% confidence interval of [29.1, 44.7] inches.

(Statement includes central tendency, data spread, and uncertainty.)

To call items back from a list type object name then $ then value i.e. `otter_ci$conf.int`

#### Now, using in-line referencing.

Mean otter length is `r round(otter_ci$estimate, 1)` inches. 

