---
title: "Lab 5"
author: "Katie Pietrucha"
date: "10/25/2021"
output: 
  html_document: 
    theme: cerulean
    toc: yes
    code_folding: hide
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals

In this section, we'll use the `t.test()` function to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values, then learn to use `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible too.

```{r}
# Create a mock sample
otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29, 90, 72, 112)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths)

# Find the standard deviation
otter_sd <- sd(otter_lengths)
```

#### What does 95% CI mean? If we took multiple samples from this population and calculated a CI for each, we would expect that 95% of CIs would contain true population mean.

Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n = 8) with a 95% confidence interval of [29.1, 44.7] inches.

(Statement includes central tendency, data spread, and uncertainty.)

To call items back from a list type object name then $ then value i.e. `otter_ci$conf.int`

#### Now, using in-line referencing.

Mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [`r round(otter_ci$conf.int[1], 1)`, `r round(otter_ci$conf.int[2], 1)`] inches.

## Part 2: Two-sample t-tests

### Example 1

Make two mock samples, and ask the question: do we have sufficient evidence to make us reject the null hypothesis that these samples were drawn from populations with the same mean?

```{r}
# Make my mock samples
oak_trees <- c(20, 19, 24, 28, 34, 12, 15, 25)
  
pine_trees <- c(39, 26, 20, 30, 37, 22, 19, 18)

# Two-sample t-test (two-sided)
trees_t <- t.test(oak_trees, pine_trees)

# Null hypothesis: mean heights are the same
# i.e.: Trees are drawn from populations with same mean height.
```

The mean heights of oak and pine trees were (X +- Y) and (X +- Y), respectively, and the difference was not significant (t(`r round(trees_t$parameter, 1)`) = `r round(trees_t$statistic, 1)`, p = `r round(trees_t$p.value, 1)`.

Format of statement: "t(df) = t-statistic, p = p-value"

Type `?t-test` in console to see definitions of values (statistic, parameter, p.value, etc.)

*AVOID:* p = 0

When things get really small (usually p < 0.001)

*Not great:* p = 0.00000012
*Better:* p < 0.001

## Part 3: Another t-test with cars data

Using the `mpg` data set.

### Take a look at the data

```{r}
compact_suv <- mpg %>%
  filter(class %in% c("compact", "suv"))

# Check for remaining levels
unique(compact_suv$class)
```

Create a histogram of city gas mileage (cty)  faceted by class starting from compact_suv.

```{r}
ggplot(data = compact_suv, aes(x=cty)) +
         geom_histogram(bins = 10) + 
  facet_wrap(~ class)

ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() +
  facet_wrap(~ class)
```

Find some summary statistics for each group.

```{r}

car_stats <- compact_suv %>%
  group_by(class) %>%
  summarize(mean_city = round(mean(cty), 2),
            sd_city = round(sd(cty), 2),
            sample_size = n())

car_stats
```

The t.test() function REALLY wants vectors of things.Use the `pull()` to pull out a vector from a data frame.

```{r}
compact_sample <- compact_suv %>%
  filter(class == "compact") %>%
  pull(cty)

# Your turn: do the same thing to get a vector of city gas mileages for SUVs

suv_sample <- compact_suv %>%
  filter(class == "suv") %>%
  pull(cty)
```

H0: Mean city gas mileages for SUVs and compact cars are the same.

```{r}
t.test(compact_sample, suv_sample)
```

There is a significant difference in mean city gas mileage for SUVs abnd compact cars (t(df) - t-statistic, p <0.001). Present along with table of values.